False Positive Probabilities for all Kepler Objects of Interest: \\ \nvalnew\ newly validated planets and \nfpnew\ likely false positives

### 2015-08-31 ms.tex
work on a new plot
more edits

These selections leave \nreliable\ KOIs for which the \vespa\ results
can be considered most reliable.  Of these, \nval\ have ${\rm FPP} <
0.01$, and are thus validated at the 99\% level.  These are not all
new validations, however, since a number of these are already
CONFIRMED.  \Fig{fpppie} shows a different kind of summary, setting
aside those with CONFIRMED and FALSE POSITIVE dispositions and
splitting up the CANDIDATES according to the \vespa\ results, showing
that \nvalnew\ KOIs are newly validated at the 99\% level.

@@

%\acrodef{fpp}[FPP]{false positive probability}
%\acrodef{koi}[KOI]{\kepler\ Object of Interest}
%\acrodefplural{koi}[KOIs]{\kepler\ Objects of Interest}
%\acrodef{nexsci}[NExScI]{NASA Exoplanet Science Institute}
%\acrodef{mcmc}[MCMC]{Markov Chain Monte Carlo}
%\acrodef{trilegal}[TRILEGAL]{TRIdimensional modeL of thE GALaxy}
%\acrodef{kic}[KIC]{Kepler Input Catalog}
%\acrodef{sdss}[SDSS]{Sloan Digital Sky Survey}
%\acrodef{ttv}[TTV]{transit timing variations}

@@

\begin{figure*}[p]
\begin{center}
\includegraphics[width=7in]{figures/fpp_summary_all.pdf}
\end{center}
\caption{False positive probabilities of all CANDIDATE or CONFIRMED
  KOIs for which we consider the \vespa\ calculations to be reliable
  (floored at $10^{-4}$ for visualization purposes), meaning they are
  considered to be reliably located on the target star ($ {\rm Pr} >
  0.99$, with ``score'' $>$ 0.4) according to pixel-level analysis
  \citep{Bryson:2015}, and have $L_{\rm tot} > 10^{-3}$, indicating
  that the hypotheses tested by \vespa\ are not all poor explanations
  of the data (see \sect{results:fpp}).  Of these \nreliable\ KOIs,
  \nval\ have FPPs less than 1\%.  Noteably, \nreliableFP\ are likely
  false positives (FPP $> 0.5$), consistent with the
  \citet{Morton:2011} and \citet{Fressin:2013} \emph{a priori}
  estimates of the overall \kepler\ candidate false positive rate.
  \figlabel{fppall}}
\end{figure*}

\begin{figure*}[p]
\begin{center}
\includegraphics[width=7in]{figures/fpp_pie.pdf}
\end{center}
\caption{A summary of how the the calculations presented in this paper
  advance our understanding of the true nature of KOIs.  More than
  half of all KOIs to date have already been dispositioned FALSE
  POSITIVE or CONFIRMED.  Those dispositioned CANDIDATE we further
  categorize according to their reliability.  The ``no reliable
  calculation'' category means that either the \vespa\ calculation was
  not successful, or that $L_{\rm tot} < 10^{-3}$.  ``On-target
  probability uncertain'' indicates that the positional probability
  calculations of \citet{Bryson:2015} are not reliable (score $<
  0.4$).  ``On-target probability $<$ 0.99'' means that the positional
  probability calculations indicate that there is a non-negligible
  chance that the source of the transit signal is not at the position
  of the KOI.  The remaining three categories are all CANDIDATE KOIs
  with reliable calculations, grouped by false positive probability.
  \nvalnew\ of these are new planet validations, and \nfpnew\ are new
  likely false positives.  \figlabel{fpppie}}
\end{figure*}

>>>>

These selections leave \nreliable\ KOIs for which the \vespa\ results
can be considered most reliable.  Of these, \nval\ have ${\rm FPP} <
0.01$, and are thus validated at the 99\% level.  These are not all
new validations, however, since a number of these are already
CONFIRMED.  \Fig{fpppie} shows a different kind of summary, grouping
KOIs by disposition and splitting up the CANDIDATES according to the
\vespa\ results, showing that \nvalnew\ KOIs are newly validated at
the 99\% level.  \Fig{rpcand} shows the radii and periods of the
CANDIDATE KOIs, grouped by FPP.

@@

In this work, we have calculated the astrophysical false positive
probability (FPP) for every \kepler\ object of interest (KOI), using
the publicly available Python module \vespa.  While the assumptions
behind this calculation are not necessarily valid for every KOI (see
\sect{results:fpp}, we have identified \nvalnew\ KOIs that have
reliable FPPs of $< 0.01$, resulting in validation of their planetary
nature at the 99\% confidence level.  The reliability of these
calculations is dependent largely on the results of \citet{Bryson:2015},
which quantify the probability that the eclipse/transit signal is
spatially coincident on the sky with the presumed target star.

These batch FPP calculations will

The \kepler\ mission has demonstrated that space-based transiting
planet surveys can identify viable planet candidates at a rate much
faster than traditional follow-up techniques can confirm them.  As a
result, probabilistic validation techniques are now

@@

\begin{figure*}[p]
\begin{center}
\includegraphics[width=7in]{figures/fpp_summary_all.pdf}
\end{center}
\caption{False positive probabilities of all CANDIDATE or CONFIRMED
  KOIs for which we consider the \vespa\ calculations to be reliable
  (floored at $10^{-4}$ for visualization purposes), meaning they are
  considered to be reliably located on the target star ($ {\rm Pr} >
  0.99$, with ``score'' $>$ 0.4) according to pixel-level analysis
  \citep{Bryson:2015}, and have $L_{\rm tot} > 10^{-3}$, indicating
  that the hypotheses tested by \vespa\ are not all poor explanations
  of the data (see \sect{results:fpp}).  Of these \nreliable\ KOIs,
  \nval\ have FPPs less than 1\% (\nvalnew\ of which have not yet been
  dispositioned as CONFIRMED).  Noteably, \nreliableFP\ are likely
  false positives (FPP $> 0.5$), consistent with the
  \citet{Morton:2011} and \citet{Fressin:2013} \emph{a priori}
  estimates of the overall \kepler\ candidate false positive rate.
  \figlabel{fppall}}
\end{figure*}

\begin{figure*}[p]
\begin{center}
\includegraphics[width=7in]{figures/fpp_pie.pdf}
\end{center}
\caption{A summary of how the the calculations presented in this paper
  advance our understanding of the true nature of KOIs.  More than
  half of all KOIs to date have already been dispositioned FALSE
  POSITIVE or CONFIRMED.  Those dispositioned CANDIDATE we further
  categorize according to their reliability.  The ``no reliable
  calculation'' category means that either the \vespa\ calculation was
  not successful, or that $L_{\rm tot} < 10^{-3}$.  ``On-target
  probability uncertain'' indicates that the positional probability
  calculations of \citet{Bryson:2015} are not reliable (score $<
  0.4$).  ``On-target probability $<$ 0.99'' means that the positional
  probability calculations indicate that there is a non-negligible
  chance that the source of the transit signal is not at the position
  of the KOI.  The remaining three categories are all CANDIDATE KOIs
  reliably confirmed to be located at the presumed target star,
  grouped by false positive probability.  \nvalnew\ of these are new
  planet validations, and \nfpnew\ are new likely false positives.
  \figlabel{fpppie}}
\end{figure*}

\begin{figure*}[p]
\begin{center}
\includegraphics[width=7in]{figures/RP_cand.pdf}
\end{center}
\caption{Periods and radii of KOIs with CANDIDATE disposition, grouped
  by FPP value.  Green circles are most likely to be planets, red X's
  are most likely to be false positives, and blue plusses have
  intermediate FPPs.  Grey dots are KOIs for which the
  \vespa\ calculation is considered less reliable.  
  \figlabel{rpcand}}
\end{figure*}
